A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Add \noindent to paragraphs following formulas

Using this function, one check if $f_1$ and $f_2$ are functionally equivalent by
computing $(f_1\overline{\oplus}f_2)\lor d$. If the result is \textbf{1}, $f_1$
and $f_2$ are functionally equivalent.

@@

The recursive procedure then has three different cases. Note that a node is only
created if no equivalent node is already present in the resultant graph.
\begin{enumerate}
    \item{
        If $n_1$ and $n_2$ are both terminal nodes, then a terminal node
        representing the value $value(n_1)\;op\;value(n_2)$ is added to the
        resultant graph and the recursion terminates.
    }
    \item{
        If either $n_1$ or $n_2$ is a nonterminal node, then:
        \begin{enumerate}
            \item{
                If $var(n_1) = var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively on $(lo(n_1), lo(n_2))$ and
                $(hi(n_1), hi(n_2))$.
            }
            \item{
                If $var(n_1)$ is a nonterminal and $n_2$ is eiter a terminal node
                or $var(n_1) < var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively on $(lo(n_1), n_2)$ and
                $(hi(n_1), n_2)$.
            }
        \end{enumerate}
    }
\end{enumerate}

>>>>

\noindent
Using this function, one check if $f_1$ and $f_2$ are functionally equivalent by
computing $(f_1\overline{\oplus}f_2)\lor d$. If the result is \textbf{1}, $f_1$
and $f_2$ are functionally equivalent.

@@

\noindent
The recursive procedure then has three different cases. Note that a node is only
created if no equivalent node is already present in the resultant graph.
\begin{enumerate}
    \item{
        If $n_1$ and $n_2$ are both terminal nodes, then a terminal node
        representing the value $value(n_1)\;op\;value(n_2)$ is added to the
        resultant graph and the recursion terminates.
    }
    \item{
        If either $n_1$ or $n_2$ is a nonterminal node, then:
        \begin{enumerate}
            \item{
                If $var(n_1) = var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively on $(lo(n_1), lo(n_2))$ and
                $(hi(n_1), hi(n_2))$.
            }
            \item{
                If $var(n_1)$ is a nonterminal and $n_2$ is eiter a terminal node
                or $var(n_1) < var(n_2)$, a node having $var(n_1)$ is created and
                the procedure is applied recursively on $(lo(n_1), n_2)$ and
                $(hi(n_1), n_2)$.
            }
        \end{enumerate}
    }
\end{enumerate}
